---
title: "EED-Development Draft Table 1"
output:
  officedown::rdocx_document: 
    tables:
      style: Table Normal
  html_notebook: default
---

```{r setup, include = F}
rm(list = ls())

knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(kableExtra)
library(stringr)
library(tableone)
library(flextable)
library(officer)
library(here)
library(labelled)
library(gtsummary)

# CoopG/tableone2flextable
tableone2flextable <- function(tableone){
  rows <- nrow(tableone)
  cols <- ncol(tableone)
  rowsXcols <- rows*cols
  colnames <- colnames(tableone)
  
  listoflists <- list()
  
  for (i in 1:cols){
    start <- (i*rows+1)-rows
    end <- i*rows
    
    listoflists[[i]] <- tableone[start:end]
  }
  
  dataframe <- as.data.frame(listoflists, col.names = colnames)
  flex <- flextable::flextable(dataframe)
  
  return(flex)
}
```

```{r}
bg <- readRDS(here('final-data/eed-dev_bg.RDS')) %>% 
  rename(hh_index = HHwealth) %>% 
  mutate(across(c(cesd_sum_t2, cesd_sum_ee_t3,
                  pss_sum_mom_t3), 
                as.numeric), 
         life_viol_any_t3 = case_when(as.character(life_viol_any_t3) == "missing" ~ NA_character_, 
                                      TRUE ~ as.character(life_viol_any_t3)) %>% 
           factor(),
         sex = factor(sex, c("female", "male")),
         country = 'Bangladesh', 
         )

k <- readRDS(here('final-data/eed-dev_k.RDS')) %>% 
  mutate(across(c(pss_score, phq_score_t3), 
                as.numeric), 
         sex = factor(sex, c("female", "male")),
         country = 'Kenya')
```

```{r}
# bg$birthord <- factor(bg$birthord, 
#                       levels = c("first", "second or greater", "missing"),
#                       ordered = TRUE)

bg$hfiacat <- factor(bg$hfiacat, 
                      levels = c("Mildly Food Insecure", "Moderately Food Insecure", 
                                 "Severely Food Insecure", "Food Secure"),
                      ordered = TRUE)

var_label(bg) <- list(# tr = "Treatment Arm", 
                      laz_t1 = "Length-for-age Z score (3 mo)", 
                      waz_t1 = "Weight-for-age Z score (3 mo)", 
                      laz_t2 = "Length-for-age Z score (14 mo)", 
                      waz_t2 = "Weight-for-age Z score (14 mo)", 
                      diar7d_t2 = "Caregiver reported diarrhea 7-day recall (3 mo)",
                      diar7d_t3 = "Caregiver reported diarrhea 7-day recall (14 mo)",
                      cesd_sum_t2 = "Depressive symptoms (CESD-R score*) at Year 1", 
                      cesd_sum_ee_t3 = "Depressive symptoms (CESD-R score*) at Year 1",
                      pss_sum_mom_t3 = "Maternal Perceived Stress Scale (PSS) at Year 2",
                      sex = "Female (%)",
                      momage = "Age (years)", 
                      momheight_raw = "Height (cm)", 
                      momedu = "Education completed", 
                      hfiacat = "Household food insecurity**"
                      # life_viol_any_t3 = "Cumulative maternal exposure to intimate partner violence",
                      # floor = "Housing material, improved floor" 
                      # birthord = "Birth Order", 
                      # Nlt18 = "Number of children < 18 years old", 
                      # Ncomp = "Total individuals in compound",
                      # watmin = "Minutes to primary water source", 
                      # walls = "Housing material, improved walls", 
                      # roof = "Housing material, improved roof", 
                      # hh_index = "Household wealth index"
                      )
```

# Table 1. Characteristics of participants in Bangladesh

```{r, tab.cap = "Bangladesh"}
bg_child <- bg %>% 
  tbl_summary(include = c(sex, laz_t1, waz_t1, 
                          laz_t2, waz_t2,
                          diar7d_t2, diar7d_t3),
              type = list(sex ~ "dichotomous"),
              value = list(sex ~ "female"),
              missing = "no")

bg_mom <- bg %>% 
  tbl_summary(include = c(momage, momheight_raw,
                          cesd_sum_t2, cesd_sum_ee_t3,
                          pss_sum_mom_t3, momedu),
              missing = "no")

bg_house <- bg %>% 
  tbl_summary(include = hfiacat,
              missing = "no")

list(bg_child, bg_mom, bg_house) %>% 
  tbl_stack(group_header = c("Child", "Mother", "Household")) %>%
  as_gt() %>%
  gt::tab_style(
    style = gt::cell_text(weight = "bold"),
    locations = gt::cells_row_groups(groups = everything())
  ) 
```


\* CESD-R = Center for Epidemiologic Studies Depression Scale Revised.

** Any level of food insecurity assessed using the Household Food Insecurity Access Scale 


```{r}
k <- k %>% 
  mutate(momedu = factor(momedu, 
                         levels = c("Primary", "IncompletePrimary", 
                                    "AnySecondary", "missing"),
                         labels = c("Primary", "Incomplete Primary", 
                                    "Any Secondary", "Missing"), 
                         ordered = T),
         hhs_mod_sev = HHS %in% c(2, 3))

var_label(k) <- list(# tr = "Treatment Arm", 
                      laz_t1 = "Length-for-age Z score (6 mo)", 
                      waz_t1 = "Weight-for-age Z score (6 mo)", 
                      laz_t2 = "Length-for-age Z score (17 mo)", 
                      waz_t2 = "Weight-for-age Z score (17 mo)", 
                      diarr7_t0 = "Caregiver reported diarrhea 7-day recall (6 mo)",
                      diarr7_t1 = "Caregiver reported diarrhea 7-day recall (17 mo)",
                      pss_score = "Maternal Perceived Stress Scale (PSS) at Year 2",
                      phq_score_t3 = "Depressive symptoms (PHQ*) at Year 2",
                      sex = "Female (%)",
                      momage = "Age (years)", 
                      momheight_raw = "Height (cm)", 
                      momedu = "Education completed", 
                      hhs_mod_sev = "Prevalence of moderate to severe household hunger**"
                      # Nlt18 = "Number of children < 18 years old", 
                      # Ncomp = "Total individuals in compound",
                      # water_time = "Minutes to primary water source", 
                      # wall = "Housing material, walls", 
                      # floor = "Housing material, floor"
                      # roof = "Housing material, roof", 
                     # hh_index = "Household wealth index"
                     )

```

# Table 2. Characteristics of participants in Kenya

```{r, tab.cap = "Kenya"}
k_child <- k %>% 
  tbl_summary(include = c(sex, laz_t1, waz_t1, 
                          laz_t2, waz_t2,
                          diarr7_t0, diarr7_t1),
              type = list(sex ~ "dichotomous"),
              value = list(sex ~ "female"),
              missing = "no")

k_mom <- k %>% 
  tbl_summary(include = c(momage, momheight_raw,
                          phq_score_t3,
                          pss_score, momedu),
              missing = "no")

k_house <- k %>% 
  tbl_summary(include = hhs_mod_sev,
              missing = "no")

list(k_child, k_mom, k_house) %>% 
  tbl_stack(group_header = c("Child", "Mother", "Household")) %>%
  as_gt() %>%
  gt::tab_style(
    style = gt::cell_text(weight = "bold"),
    locations = gt::cells_row_groups(groups = everything())
  ) 
```


\* PHQ = Patient Health Questionnaire 

** Moderate to severe hunger defined using the Household Hunger Scale